Generalists are the most urban-tolerant of birds: a phylogenetically controlled analysis of ecological and life-history traits using a novel continuous urbanization index

### 2018-06-04 ms.Rmd
changed the title.

---
title: "A continental-scale analysis finds generalists, with large clutch size and residual brain mass, are the most urban-tolerant of birds"

>>>>

---
title: "Generalists are the most urban-tolerant of birds: a phylogenetically controlled analysis of ecological and life-history traits using a novel continuous urbanization index"
